%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Phi}{Nguyen}
{ \urlstyle{same}\href{https://phinguyen.dev}{phinguyen.dev }| \href{https://github.com/pnguy55}{ My GitHub}\\
\href{mailto:phi@phinguyen.dev}{phi@phinguyen.dev} | 225-205-6210
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
(With linked examples)
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\location{BACK END-----------}
{\bf JavaScript} ( Node, Express )\\
\textbullet{} \href{https://stoolstory.com}{ StoolStory ( Mongo - NoSQL )}\\
\textbullet{} \href{https://myvideotagger.com}{ MyVideoTagger ( Mongo - NoSQL )}\\

{\bf Java} (Spring Boot)\\
\textbullet{} \href{https://calculator-react-spring.herokuapp.com/}{ Calculator(Spring Boot & Postgres)}\\
{\bf SQL} \\
\textbullet{} Internal SAP Hana Data migrations\\

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\location{FRONT END----------}
{\bf JavaScript} ( Vanilla, React, UI5 )\\
\textbullet{} \href{https://phinguyen.dev}{ Portfolio ( Next )}\\
\textbullet{} \href{https://stoolstory.com}{ StoolStory ( React )}\\
\textbullet{} \href{https://myvideotagger.com}{ MyVideoTagger ( React )}\\
\textbullet{} \href{https://calculator-react-spring.herokuapp.com/}{ Calculator (React)}\\
\textbullet{} Internal data migration dashboards (UI5)

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\location{Also comfortable with/Learning:}
C \textbullet{} C\# \textbullet{} CSS \textbullet{} SASS \textbullet{} Python \\
Android \textbullet{} Flutter \textbullet{}

\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IBM}
\descript{Apprenticeship - \\}
\location{Application Development\\}
\location{2019 | Complete}
\sectionsep

\subsection{Louisiana State University}
\descript{90 Credits towards CS}
\location{Incomplete}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Course Work}

\subsection{Apprenticeship}
Agile Software Development  \\
Full Stack JavaScript \\
Relational Database Management \\
API Development \\
React & Redux Development \\
CS50 Harvard Course \\
Cloud Computing \\
SAP Data Migration \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\subsection{Undergraduate}
Data Structures and Algorithms \\
Object Oriented Programming  \\
Video Game Design \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{IBM}
\descript{| Software Engineer / Data Engineer}
\location{June 2019 - Present | Baton Rouge, LA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item My current position involves building data migration tools and performing ETL data migrations. I've created automated migration processes myself, as well as supplement other more complex migrations processes with dashboards written in JavaScript (UI5) and SQL within the Hana XS ecosystem that show insights and allow upkeep of data through web interfaces.

\item Client accomplishments listed below.
\end{tightemize}
\sectionsep

\runsubsection{Murphy Law Firm}
\descript{| Full Stack JavaScript Developer }
\location{Aug 2018 – Jul 2019 | Baton Rouge, LA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Saved the business thousands of dollars in advertising costs by bringing marketing in house with a nearly 200\% increase in revenue.
\item Led a small team, 1 developer intern and 2 graphic designers to deliver multiple web projects.
\item Wrote and reviewed code for JS - jQuery, Front-End and PHP backend .
\href{https://murphylawfirm.com}{\bf Murphylawfirm.com}
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects and Accomplishments}
\runsubsection{Deluxe Corp. -}
\descript{IBM Client}
Developed a JavaScript/SQL solution to help Deluxe keep their revenue records up to date as their data migration was performed over the course of the next year.
\sectionsep

\runsubsection{Norfolk Southern -}
\descript{IBM Client}
Led the development of a passive data governance tool with JavaScript and SQL to keep their Hana database up to date.  They were be able to check the tool and run a series of business rules to determine if their data was clean.
\sectionsep

\runsubsection{Stoolstory.com -}
\descript{Personal Project}
Web application that allows the user to make log their health data to present to a health professional and for instant analysis as well as general record keeping. \\
\href{https://stoolstory.com}{\bf StoolStory.com}
\sectionsep


\href{https://myvideotagger.com}{\runsubsection{MyVideoTagger.com -}}
\descript{Personal Project}
Personal project that allows content creators to pull tags from similiar youtube videos to add to their own.  Users can log in with  oAuth and save their taglists to their personal account. \\
\href{https://myvideotagger.com}{\bf MyVideoTagger.com}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
